%% 
%%  A DANTE-Edition example
%% 
%%  Example 36-00-8 on page 772.
%% 
%%  Copyright (C) 2011 Herbert Voss
%% 
%%  It may be distributed and/or modified under the conditions
%%  of the LaTeX Project Public License, either version 1.3
%%  of this license or (at your option) any later version.
%% 
%%  See http://www.latex-project.org/lppl.txt for details.
%% 
%% 
%% ==== 
% Show page(s) 1
%% 
\documentclass[]{article}
\pagestyle{empty}
\setlength\textwidth{375.57637pt}
\setlength\parindent{0pt}

\usepackage{pstricks,shapepar}
\newsavebox\PBox

\begin{document}
\savebox\PBox{%
\begin{minipage}{10cm}
\shapepar{\nutshape}
A great many people have never heard the scream of an eagle. The only
voice they connect with the kind of the air is a ludicrously feeble
squawk, dim with distance, but in his great moments the eagle has a
war-cry like that of the hawk, but harsher, hoarser, tenfold in volume.
This sound cut into the night in the gulch, and Vic Gregg started and
glanced about for echoes made the sound stand at his side; then he
looked up, and saw two eagles fighting in the light of the morning. He
knew what it meant--the beginning of the mating season, and these two
battling for a prize. They darted away. They flashed together with
reaching talons and gaping beaks, and dropped in a tumult of wings,
then soared and clashed once more until one of them folded his wings and
dropped bulletlike out of the morning into the night. Close over Gregg's
head, the wings flirted out--ten feet from tip to tip--beat down with
a great washing sound, and the bird shot across the valley in a level
flight. The conqueror screamed a long insult down the hollow. For a
while he balanced, craning his bald head as if he sought applause, then,
without visible movement of his wings, sailed away over the peaks. A
feather fluttered slowly down past Vic Gregg.
\end{minipage}}
\psset{unit=0.6}
\begin{pspicture}(-6,-5.5)(6,5.5)
  \rput(0.6,0){\psscalebox{0.6}{\usebox\PBox}}
  \pscustom[fillstyle=solid,fillcolor=blue]{%
    \psarc(0,1.1){1.1}{270}{450}
    \psarc(0,0){2.2}{90}{270}
    \psarcn(0,-1.1){1.1}{270}{450}
  }
  \pscircle*[linecolor=blue](0,-1.1){0.3}
  \pscircle[fillstyle=solid](0,1.1){0.3}
%  \psarc(0,0){2.2}{270}{450}
\end{pspicture}
\end{document}
